Programming Language Survey Paper on Haskell

### 2013-04-22 projects/term_paper/paper.tex
Added material on introspection and reflection.

\section{Introduction}
This paper provides an overview of the Haskell programming language.

@@

\subsubsection{Operators and Precedence}
\bi
    \item Operators: postfix notation, naming typically consists of symbols
    \item Functions: infix notation, named using alphanumeric characters in camel case
    \item Any function can be used as an operator by calling it in postfix notation
\begin{minted}{haskell}
f :: (Int a) => a -> a -> a
f a b = a + b
; invoke the function in postfix notation
print (1 `f` 2)
\end{minted}
    \item Any operator can be called as a function in infix notation
\begin{minted}{haskell}
print ((+) 2 5)
\end{minted}
    \item Operators can be overloaded
\begin{minted}{haskell}
(*) :: (Num a) => a -> a -> a
(*) a b = a * a * b
print (2 * 3)
\end{minted}
\ei

@@

\subsubsection{Scoping}
In Haskell, static scoping is employed for

@@

\section{Advanced Topics}

\subsection{Inheritance}
\subsection{Concurrency Support}
\subsection{Introspection}

>>>>

\section{Introduction}
This paper provides an overview of the Haskell programming language.  The sections are outlined as follows:
section 1 describes the background surrounding Haskell, including its connections to functional programming,
and its usage today.  Section 2 provides a survey of many of the data and control constructs native to Haskell.
Section 3 presents a brief look at several extensions beyond the Haskell core.

@@

\subsubsection{Operators and Precedence}
\bi
    \item Operators: postfix notation, naming typically consists of symbols
    \item Functions: infix notation, named using alphanumeric characters in camel case
    \item Any function can be used as an operator by calling it in postfix notation
\begin{minted}{haskell}
f :: (Int a) => a -> a -> a
f a b = a + b
; invoke the function in postfix notation
print (1 `f` 2)
\end{minted}
    \item Any operator can be called as a function in infix notation
\begin{minted}{haskell}
print ((+) 2 5)
\end{minted}
    \item Operators can be overloaded
\begin{minted}{haskell}
(*) :: (Num a) => a -> a -> a
(*) a b = a + a + a + a
print (2 * 3)
\end{minted}
\ei

@@

\subsubsection{Scoping}
In Haskell, static scoping is employed.  As such, bindings are localized
to the function in which they were defined or passed.

@@

\section{Advanced Topics}
Beyond the basic data and control structures discussed to this point,
Haskell contains a wide array of constructs, extension modules, and
and other features.  This section considers the following advanced
topics: inheritance, concurrency, and runtime type checking.

\subsection{Inheritance}

\subsection{Concurrency Support}

\subsection{Introspection and Reflection}
As mentioned previously, Haskell posesses a strong static type system
implented at compile time. As such, the Haskell '98 language definition
does not provide support for runtime type examination or manipulation
(i.e., introspection and reflection, respectively).  However, effors have been
made toward adding support similar to these features:
\bi
    \item Scrap your boilerplate: generic programming~\cite{haskell-syb}
    \item Template Haskell: an extension module for compile-time metaprogramming~\cite{haskell-th}
\ei
